Combining information from photometric and spectroscopic data:\\ propogating uncertainties in spectrophotometric calibration

### 2015-04-30 tex/ms.tex
working joint posterior plotting
fix bugs in uncertainties plotting for dashboards and in setting the speccal directory in paramfiles, add text about photometry beyond the spectra even with perfect spec cal

\subsection{Mock Data}
Our mock data are designed to mimic the actual data as much as
possible.  Mock spectra and photometry are generated from the model
described in below (\S\ref{sec:cluster_model}, equation
\ref{eq:MeanModel}) for a given set of parameters $\theta^\prime$.  We
then convolve the spectrum with an instrumenal LSF, interpolate onto
the observed wavelength scale and add noise according to the SNR of
the real data.  For the photometry we assume a SNR of 10.  We also
mask the mock spectra at the location of significant sky lines and ISM
lines that are present in the real data.

@@

\subsection{Star Cluster Model}
\label{sec:cluster_model}
We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by a vector
\begin{eqnarray}\displaystyle
f_{\theta_s}(\lambda_o) & = &
\frac{m_*}{4\pi d_L^2(1+z)} \, L(\sigma_*, z) \, s(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V} \\
\nonumber \\ 
\lambda_o & = & (1+z)\,\lambda 
\\
\theta_s & \equiv & \left[ m_*, t, Z, \tau_V, z, d_L, \sigma_*, \beta \right]
\quad ,
\end{eqnarray} where the
parameters $\theta_s$ include 
the stellar mass $m_*$, 
effective optical depth to dust in the $V$-band $\tau_V$, 
luminosity distance $d_L$,
and redshift $z$.
The matrix $L(\sigma_*, z)$ is a convolution kernel representing the
stellar velocity profile,
and $\sigma_*$ is the stellar velocity dispersion. 
The shape of the dust attenuation curve is given by $k_\lambda \equiv
\tau_\lambda/\tau_V$.  
The observed frame wavelengths $\lambda_o$ are related to the
restframe wavelengths $\lambda$ in the usual way.

@@

The final mean model is then given by the convolution in wavelength
\begin{eqnarray}\label{eq:MeanModel} 
\mu(\theta) &  = & L(\sigma_{inst}) \, \left[ f_{\theta_s}(\lambda_o)
                   + f_{\theta_g}(\lambda_o) \right]\\
f_{\theta_g}(\lambda_o) & = & L(\sigma_{gas}, z) \,  \{a_\ell\delta(\lambda-\lambda_\ell)\}\\
\theta & \equiv & \left[ \{\theta_s\}, \{\theta_{g}\}, \sigma_{inst} \right]
\quad ,
\end{eqnarray}
where the matrix $L(\sigma_{inst})$ represents the convolution kernel
for the instrumental linespread function parameterized by
$\sigma_{inst}$,
and the full parameter set $\theta$ now includes
the instrumental broadening $\sigma_{inst}$ 
and the gas-phase parameters $\theta_g$.
This is the mean model which appears in equation
\ref{eq:spectroscopicLF}.

@@

We have demonstrated, using using both mock and real spectra of
galactic stellar clusters, that we can combine photometric and
spectroscopic data in a principled way to infer physical properties.
We do not resort to an arbitrary down-weighting or up-weighting of
certain data. Instead, we explicitly model our uncertain knowledge of
the spectral calibration and infer this calibration jointly with the
physical properties. For a number of applications this combination of
spectroscopy and photometry reduces the need for spectrophotometric
calibration entirely, such that the less expensive photometric
calibration is sufficient.  Additional calibration information, if it
exists, can be incorporated into informative priors on the calibration
parameters of the model, inform the construction of the calibration
model (including the form of the covariance kernel), or approximately
remove gross features that are difficult to model parametrically or
via a Gaussian Process.  {\color{blue} Discuss more complicated
covariance kernels, multiple kernels}

{\color{blue} BDJ words about the gains that might be made by
including photometry over a large range in wavelength with spectroscopy
over relatively small ranges.}

>>>>

\subsection{Mock Data}
Our mock data are designed to mimic the actual data as much as
possible.  Mock spectra and photometry are generated from the model
described in below (\S\ref{sec:cluster_model}, equation
\ref{eq:StarModel}) for a given set of parameters $\theta_s$.  We then
convolve the spectrum with an instrumenal LSF, interpolate onto the
observed wavelength scale and add noise according to the SNR of the
real data.  For the photometry we assume a SNR of 10.  We also mask
the mock spectra at the location of significant sky lines and ISM
lines that are present in the real data.

@@

\subsection{Star Cluster Model}
\label{sec:cluster_model}
We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by a vector
\begin{eqnarray} \label{eq:StarModel}\displaystyle
f_{\theta_s}(\lambda_o) & = &
\frac{m_*}{4\pi d_L^2(1+z)} \, L(\sigma_*, z) \, s(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V} \\
\nonumber \\ 
\lambda_o & = & (1+z)\,\lambda 
\\
\theta_s & \equiv & \left[ m_*, t, Z, \tau_V, z, d_L, \sigma_*, \beta \right]
\quad ,
\end{eqnarray} where the
parameters $\theta_s$ include 
the stellar mass $m_*$, 
effective optical depth to dust in the $V$-band $\tau_V$, 
luminosity distance $d_L$,
and redshift $z$.
The matrix $L(\sigma_*, z)$ is a convolution kernel representing the
stellar velocity profile,
and $\sigma_*$ is the stellar velocity dispersion. 
The shape of the dust attenuation curve is given by $k_\lambda \equiv
\tau_\lambda/\tau_V$.  
The observed frame wavelengths $\lambda_o$ are related to the
restframe wavelengths $\lambda$ in the usual way.

@@

The final mean model is then given by the convolution in wavelength
\begin{eqnarray}\label{eq:MeanModel} 
\mu(\theta) &  = & L(\sigma_{inst}) \, \left[ f_{\theta_s}(\lambda_o)
                   + f_{\theta_g}(\lambda_o) \right]\\
f_{\theta_g}(\lambda_o) & = & L(\sigma_{gas}, z) \,  \{a_\ell\delta(\lambda-\lambda_\ell)\}\\
\theta & \equiv & \left[ \{\theta_s\}, \{\theta_{g}\}, \sigma_{inst} \right]
\quad ,
\end{eqnarray}
where the matrix $L(\sigma_{inst})$ represents the convolution kernel
for the instrumental linespread function parameterized by
$\sigma_{inst}$,
and the full parameter set $\theta$ now includes
this instrumental broadening $\sigma_{inst}$ 
and the gas-phase parameters $\theta_g$.
This is the mean model which appears in equation
\ref{eq:spectroscopicLF}.

@@

We have demonstrated, using using both mock and real spectra of
galactic stellar clusters, that we can combine photometric and
spectroscopic data in a principled way to infer physical properties.
We do not resort to an arbitrary down-weighting or up-weighting of
certain data. Instead, we explicitly and flexibly model our uncertain
knowledge of the spectral calibration and infer this calibration
jointly with the physical properties. For a number of applications
this combination of spectroscopy and photometry reduces the need for
spectrophotometric calibration entirely, such that the less expensive
photometric calibration is sufficient.  Additional calibration
information, if it exists, can be incorporated into informative priors
on the calibration parameters of the model, inform the construction of
the calibration model (including the form of the covariance kernel),
or approximately remove gross features that are difficult to model
parametrically or via a Gaussian Process.  {\color{blue} Discuss more
complicated covariance kernels, multiple kernels.}

{\color{blue} BDJ words (and experiments?) about the gains that might
be made by including photometry over a large range in wavelength with
spectroscopy over relatively small ranges.}  In this case even with
perfectly known spectrophotometric calibration, the photometry would
in principle add information.  This would occur if models with very
similar spectra in the observed range had differing SEDs outside that
range.
